Proposed Solution

### 2017-01-22 CAV17/secs/eval.tex
strucutre for evaluation

\begin{table}[h]
\centering
\caption{Results of Learning}
\label{table-training}
\begin{tabular}{|c|c|c|c|}
\hline
{\bf Class of Error } & {\bf Total Rules Learned from Training Set} & {\bf Rules Detected on Benchmark set} & {\bf Thresholds}\\ 
\hline
\hline
10   & 2.997     & &  \\ \hline
50   & 46.4208   & &  \\ \hline
100  & 206.7798  & &  \\ \hline
150  & 431.7772  & &  \\ \hline
200  & 856.6383  & &  \\ 
\hline
\end{tabular}
\end{table}

\begin{table}[h]
\centering
\caption{Training time for different datasets}
\label{table-training}
\begin{tabular}{|c|c|c|}
\hline
{\bf The \# of Files for Training} & {\bf Training Time ConfigC (sec.)} & {\bf Training Time \app (sec.)}\\ 
\hline
\hline
10   & 2.997     &   \\ \hline
50   & 46.4208   &   \\ \hline
100  & 206.7798  &   \\ \hline
150  & 431.7772  &   \\ \hline
200  & 856.6383  &   \\ 
\hline
\end{tabular}
\end{table}

>>>>

We evaluate this approach using our implementation, \app.
We use two training sets, a preexisting set of MySQL configuration from~\cite{xu15systems} of 256 files,
 and our own set of collected MySQL configuration from Github of 1120 files.
In our evaluation we focus on MySQL for consistency, but any configuration language (that can be parsed to the intermediate representation from Sec.~\ref{sec:trans}) can be used.

We run \app on 80\% as our collected configuration files, selected at random, as a training set to generate rules.
The remaining 20\% is used as a testing set to be verified by the learned rules.
We report the number of rules learned and number of errors detected in Table~\ref{table:learning}.
Note that in contrast to program verification, we do not have an oracle for determining if a reported error is a true error, or a false positive.
When learning a specification for a program, that specification can be checked by violating said specification and testing the program.
Because misconfigurations are dependent on the rest of the system, the available hardware, and the usage patterns, we cannot simulate the all conditions to determine if a reported error will cause system failure.
Indeed, as evidenced by Example~\ref{ex:fine}, some misconfigurations will only cause greater than expected performance degradation.
In this case, the very definition of a true error is necessarily imprecise.

\begin{table}[h]
\centering
\caption{Results of Learning}
\label{table:learning}
\begin{tabular}{|c|c|c|c|c|}
\hline
{\bf Class of Error } & {\bf \# Rules Learned} & {\bf \# Rules Detected} & {\bf Support} & {\bf Confidence}\\ 
\hline
\hline
Order        & 2.997     & &  & \\ 
Missing      & 46.4208   & &  & \\ 
Type         & 206.7798  & &  & \\ 
Fine-Grain   & 431.7772  & &  & \\ 
Coarse-Grain & 856.6383  & &  & \\ 
\hline
\end{tabular}
\end{table}

The errors reported may have a varying impact on the system, ranging from failing to start, runtime crash, or performance degradation.
Since this is a probablistic system, it is also that some errors are false positives, a violation of the rule has no effect on the system.
It it therefore desirable to sort the reported errors in order of severity. 
To achieve this we use the post analysis metric described in Sec.~\ref{sec:ruleorder}.
To estimate the impact of this metric, we track the rank of known true positives with, and without, the augmented rule ordering in Table~\ref{table:order}.

\begin{table}[h]
\centering
\caption{Effect of Post Analysis Rule Ordering for known true positives}
\label{table:order}
\begin{tabular}{|c|c|c|c|}
\hline
{\bf Class of Error} & {\bf Reference} & {\bf Rank w/o} & {\bf Rank w/} \\
\hline
\hline
Order        & Ex.~\ref{ex:order}   & & \\ 
Missing      & Ex.~\ref{ex:miss}    & & \\ 
Type         & Ex.~\ref{ex:type}    & & \\ 
Fine-Grain   & Ex.~\ref{ex:fine}    & & \\ 
Coarse-Grain & Ex.~\ref{ex:coarse}  & & \\ 
\hline
\end{tabular}
\end{table}

The checker stage of \app is the only one facing an end user that wants to verify a new configuration file.
However, the user may also want to interface with the previous stages as well. 
We have only build rules for MySQL, a relatively well documented language, but any configuration language can be analyzed with \app given a training set.
In this case, the user will need to rebuild the rule set.
A user also may want to update the support of confidence threshold to report more or fewer error, as is needed for their application.
It is then important that the learning process is reasonably fast.
The times reported in Table~\ref{table:training} were run on a single thread of a Intel i5-3450 CPU @ 3.10GHz with 16GB of RAM.

\begin{table}[h]
\centering
\caption{Training time for different datasets}
\label{table:training}
\begin{tabular}{|c|c|c|}
\hline
{\bf The \# of Files for Training} & {\bf ConfigC Training Time (s)} & {\bf \app Training Time (s)}\\ 
\hline
\hline
10   & 2.997     &   \\ \hline
50   & 46.4208   &   \\ \hline
100  & 206.7798  &   \\ \hline
150  & 431.7772  &   \\ \hline
200  & 856.6383  &   \\ 
\hline
\end{tabular}
\end{table}

### 2017-01-22 CAV17/secs/learner.tex
strucutre for evaluation

With the learned rules and constraints in hand (generated
by the learner module),
\app checks whether any entry in a target configuration file
violates the learned rules and constraints.
For a given configuration file, \app parses it the same
way employed in the translator, thus obtaining a structured
and typed representation for the target configuration file.
Then, the checker uses two sub-modules (shown in 
Figure~\ref{fig-overview}) to check the target
configuration file based on rules and constraints.

>>>>

With the learned rules generates by the learner module,
  \app checks whether any entry in a target configuration file violates the learned rules and constraints.
\app parses a verification target configuration file the same way employed in the translator for learning,
  obtaining a structured and typed representation.
Then, the checker applies the learner to build the set of relations observed in the file.
For any relation that violates a known rule, the checker will output the predicate and keyword sets associated with that rule, as well as the learned support and confidence values.
Since the tool is probabilistic, we provide the user with these values to determine if they rule must be satisfied in their application on a case-by-case basis.
For instance, the \texttt{key\_buffer} misconfiguration from Sec. \ref{ex:fine} will only be noticeable if the application experiences a heavy traffic load, so the user may choose to ignore this error if they are confident this will not be an issue.

### 2017-01-22 CAV17/secs/postanal.tex
strucutre for evaluation

VeriConf can output the series of learned rules extracted from its training
set as described in $\S$\ref{sec-learn}.

\subsection{Rule Ordering}

>>>>

VeriConf can output the set of learned rules from the training set as described in $\S$\ref{sec-learn}.
Note that the ability to inspect the learned rule set is a special property of this technique.
The core task, building a model from unlabeled examples to classify files as either correct or incorrect, is also a classic problem for other machine learning techniques such as neural networks~\cite{nn1,nn2,nn3}.
When applying machine learning to verification of configuration files, this is not, however, an ideal approach.
The resulting model from a neural network is easily not amenable to analysis~\cite{nnAnalysis1,nnAnalysis2}.
The simple structure of rules with weights from an association rule learning-like approach, will instead allows us to do further inference on the resulting model.

\subsection{Rule Ordering}
\label{sec:ruleorder}
